---
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
  output: html_notebook
  word_document: 
    fig_caption: yes
    md_extensions: +tex_math_single_backslash
    reference_docx: knit_to_docx_style.docx
  html_document:
    df_print: paged
author: N. Tsutsumida^\*,1^
title: TITLE 
csl: elsevier-harvard.csl
preamble: |
  - \usepackage{amsmath,amssymb}
  - \usepackage{mathspec}
  - \usepackage{indentfirst}
  - \usepackage{graphicx}
  - \usepackage{calc}
  - \parindent = 1em
  - \usepackage{zxjatype}
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{float}
  - \usepackage{caption}
  - \usepackage{mathop}
  - \captionsetup[figure]{labelformat=empty}
  - \captionsetup[table]{labelformat=empty}
classoption: xelatex,ja=standard
bibliography: bib_example.bib
---

```{r knit_setup, eval=TRUE, include=FALSE}
options(scipen=10)

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(cache = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(error = FALSE)
knitr::opts_chunk$set(message = FALSE)

set.seed(1118)
```


```{r libraries, include=FALSE}
library(shiny)
library(leaflet)
library(sf)
library(sp)
library(tidyverse)
library(shinydashboard)
library(here)
library(stars)
library(tmap)
library(GWmodel)
```

## Abstract
- how to write a paper(https://www.nature.com/nature-research/for-authors/write)
- http://www-mech.eng.cam.ac.uk/mmd/ashby-paper-V6.pdf

## Keywords
AAAAAAAAAAAAAAAAAAAAAAAAAAAAAA.

## 1.Introduction
AAAAAAAAAAAAAAAAAAAAAAAAAAAAAA.  
AAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAA.

## 2.Methods
AAAAAAAAAAAAAAAAAAAAAAAAAAAAAA.  
AAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAA.

## 3.Study area
AAAAAAAAAAAAAAAAAAAAAAAAAAAAAA.  
AAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAA.

## 4.Results
AAAAAAAAAAAAAAAAAAAAAAAAAAAAAA.  
AAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAA.

## 5. Discussion
AAAAAAAAAAAAAAAAAAAAAAAAAAAAAA.  
AAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAA.

## 6. Conclusions
AAAAAAAAAAAAAAAAAAAAAAAAAAAAAA.  
AAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAA.

## Acknowledgements
AAAAAAAAAAAAAAAAAAAAAAAAAAAAAA.  
AAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAA.

## Appendix
AAAAAAAAAAAAAAAAAAAAAAAAAAAAAA.  
AAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAA.

## References

